MT Field Site Analysis Report

### 2024-05-13 qmd/projects/msu/wss/field_report.qmd
commit 5/13 2024

---
title: "MT Field Site Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  html:
    # layout: sidebar
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_expand: true
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
toc: true
toc_title: "Table of Contents"
# toc_expand: true
# toc_float: true
---
<!-- field site cover image -->
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Cropping Example</title>
<style>
    }
    .image-container {
        width: auto; /* Set the width of the container */
        height: auto; /* Set the height of the container */
        overflow: hidden; /* Hide overflow */
    }
    .image-container img {
        width: 100%; /* Make the image fill the container horizontally */
        height: auto; /* Maintain aspect ratio */
        object-fit: cover;
        object-position: center;
    }
</style>
</head>
<body>

@@

</body>
</html>

```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

@@

raw.2023 <-
read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/field Sites/2023/2023\ Field Site\ Data.xlsx", sheet = "n.infested") %>%
  mutate(year = "2023") 
```
```{r (stubble.####) stubble data, echo = F}
stubble.2023 <-
  read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/field Sites/2023/2023\ Field Site\ Data.xlsx", 
           sheet = "stubble") %>%
  dplyr::select(-name) %>%
  na.omit() %>%
  mutate(year = "2023")

@@

```
```{r (joined.stubble) stubble join, echo = F}
# the below code joins the 2022 and 2023 stubble data frames
joined.stubble <-
stubble.2023 %>%
  dplyr::select(site, location, distance,
                inf.nc, cut, cocoon, eh, total, year) %>%
  mutate(collection = "fall") %>% 
  rbind(stubble.2022 %>%
          dplyr::select(site, year, location, distance, collection,
                        inf.nc, cut, cocoon, eh, total)) %>%
  # remove N sites and re add as NS and NN for example
  group_by(site, location, year, distance, collection) %>%
  mutate(inf = sum(cut, inf.nc, cocoon, eh)) %>%
  # first, we remove the site arguement by grouping by everything else
  group_by(site, location, year, distance, collection) %>%
  dplyr::select(-c(inf.nc)) %>%
  rename("e" = eh,
         "c" = cocoon) %>%
  mutate(p.inf = inf/total,
         p.par = (c + e)/inf,
         p.cut = cut/inf,
         poten = (cut + e + c)/inf)

@@

```
```{r (n.inf) brome join, echo = F}
n.inf <-
raw.2023 %>%
  dplyr::select(site, year, location, collection, 
              n.uv, n.ur, n.iv, n.ir, n.ix, 
              cut, e, c)  %>%
  bind_rows(raw.2022 %>%
              rename(n.uv = uv,
                     n.ur = ur,
                     n.iv = iv,
                     n.ir = ir,
                     n.ix = ix) %>%
              dplyr::select(site, year, location, collection, 
                    n.uv, n.ur, n.iv, n.ir, n.ix, 
                    cut, e, c)) %>%
  group_by(site, location, collection, year) %>%
  mutate(inf = sum(n.iv, n.ir, n.ix),
         total = sum(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  ungroup() %>%
  dplyr::select(-c(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  mutate(p.inf = inf/total,
         p.par = (c + e)/inf,
         p.cut = cut/inf,
         poten = (cut + c + e)/inf) %>%
  pivot_longer(-c(site, location, collection, year),
               names_to = "type",
               values_to = "value") %>%
  group_by(location, collection, year, type) %>%
  distinct() %>%
  mutate(distance = "brome",
         location = case_when(
           location == "kw" ~ "k",
           location == "ke" ~ "k", 
           TRUE ~ location))
```
```{r (stubble.brome) join stubble/brome, echo = F}
# join the stubble data and the brome data
stubble.brome <-
joined.stubble %>%
  pivot_longer(-c(site, location, distance, year, collection),
               names_to = "type",
               values_to = "value") %>%
  distinct() %>%
  rbind(n.inf) %>%  # rbind the brome data
  filter(!type == "total") %>%  # remove type = "total"
  mutate(type = case_when(
    type == "c" ~ "p",
    type == "e" ~ "p",
    TRUE ~ type)) %>% # replace the e and c variables with p, for simplicity
  ungroup() %>%
  dplyr::select(-site) %>%
  group_by(location, distance, year, collection, type) %>%
  reframe(mean = mean(value),
         count = n(),
         sd = sd(value),
         se = sd/sqrt(count)) %>%
  distinct() %>%
  filter(type %in% c("p.inf", "p.cut", "p.par", "poten")) %>%
  distinct()
```
```{r, echo = F, eval = F}
stubble.brome %>%
  filter(location == "g",
         distance %in% c("20", "5"),
         year == "2023",
         collection == "fall")
```

@@

</body>
</html>
```

<!-- ![North Road, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/nnns-min.png?raw=true) -->

**Note:**    
- In 2023, the field south of North Road was fallow, so no stubble infestation data was collected from the field south of North Road.

@@

</body>
</html>
```

<!-- ![Gardiner Road, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/gardiner%20road-min.png?raw=true) -->

@@

</body>
</html>
```

<!-- ![Harvest & Sunset Road Instersection, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/harvest%20road-min.png?raw=true) -->

@@

</body>
</html>
```

<!-- ![Kolin Road, Moccasin, MT (2023)](https://github.com/jstrand894/Website/blob/main/kolin%20road-min.png?raw=true) -->

>>>>

---
title: "MT Field Site Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  html:
    # layout: sidebar
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_expand: true
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
toc: true
toc_title: "Table of Contents"
# toc_expand: true
# toc_float: true
---

<!-- field site cover image -->

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Cropping Example</title>
<style>
    }
    .image-container {
        width: auto; /* Set the width of the container */
        height: auto; /* Set the height of the container */
        overflow: hidden; /* Hide overflow */
    }
    .image-container img {
        width: 100%; /* Make the image fill the container horizontally */
        height: auto; /* Maintain aspect ratio */
        object-fit: cover;
        object-position: center;
    }
</style>
</head>
<body>

@@

</body>
</html>
```
```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```

```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

@@

raw.2023 <-
read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/field Sites/2023/2023\ Field Site\ Data.xlsx", sheet = "n.infested") %>%
  mutate(year = "2023") 
```

```{r (stubble.####) stubble data, echo = F}
stubble.2023 <-
  read_excel("/Users/jacksonstrand/Library/CloudStorage/OneDrive-MontanaStateUniversity/Data/BWW/Field/field Sites/2023/2023\ Field Site\ Data.xlsx", 
           sheet = "stubble") %>%
  dplyr::select(-name) %>%
  na.omit() %>%
  mutate(year = "2023")

@@

```{r (joined.stubble) stubble join, echo = F}
# the below code joins the 2022 and 2023 stubble data frames
joined.stubble <-
stubble.2023 %>%
  dplyr::select(site, location, distance,
                inf.nc, cut, cocoon, eh, total, year) %>%
  mutate(collection = "fall") %>% 
  rbind(stubble.2022 %>%
          dplyr::select(site, year, location, distance, collection,
                        inf.nc, cut, cocoon, eh, total)) %>%
  # remove N sites and re add as NS and NN for example
  group_by(site, location, year, distance, collection) %>%
  mutate(inf = sum(cut, inf.nc, cocoon, eh)) %>%
  # first, we remove the site arguement by grouping by everything else
  group_by(site, location, year, distance, collection) %>%
  dplyr::select(-c(inf.nc)) %>%
  rename("e" = eh,
         "c" = cocoon) %>%
  mutate(p.inf = inf/total,
         p.par = (c + e)/inf,
         p.cut = cut/inf,
         poten = (cut + e + c)/inf)

@@

```{r (n.inf) brome join, echo = F}
n.inf <-
raw.2023 %>%
  dplyr::select(site, year, location, collection, 
              n.uv, n.ur, n.iv, n.ir, n.ix, 
              cut, e, c)  %>%
  bind_rows(raw.2022 %>%
              rename(n.uv = uv,
                     n.ur = ur,
                     n.iv = iv,
                     n.ir = ir,
                     n.ix = ix) %>%
              dplyr::select(site, year, location, collection, 
                    n.uv, n.ur, n.iv, n.ir, n.ix, 
                    cut, e, c)) %>%
  group_by(site, location, collection, year) %>%
  mutate(inf = sum(n.iv, n.ir, n.ix),
         total = sum(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  ungroup() %>%
  dplyr::select(-c(n.uv, n.ur, n.iv, n.ir, n.ix)) %>%
  mutate(p.inf = inf/total,
         p.par = (c + e)/inf,
         p.cut = cut/inf,
         poten = (cut + c + e)/inf) %>%
  pivot_longer(-c(site, location, collection, year),
               names_to = "type",
               values_to = "value") %>%
  group_by(location, collection, year, type) %>%
  distinct() %>%
  mutate(distance = "brome",
         location = case_when(
           location == "kw" ~ "k",
           location == "ke" ~ "k", 
           TRUE ~ location))
```

```{r (stubble.brome) join stubble/brome, echo = F}
# join the stubble data and the brome data
stubble.brome <-
joined.stubble %>%
  pivot_longer(-c(site, location, distance, year, collection),
               names_to = "type",
               values_to = "value") %>%
  distinct() %>%
  rbind(n.inf) %>%  # rbind the brome data
  filter(!type == "total") %>%  # remove type = "total"
  mutate(type = case_when(
    type == "c" ~ "p",
    type == "e" ~ "p",
    TRUE ~ type)) %>% # replace the e and c variables with p, for simplicity
  ungroup() %>%
  dplyr::select(-site) %>%
  group_by(location, distance, year, collection, type) %>%
  reframe(mean = mean(value),
         count = n(),
         sd = sd(value),
         se = sd/sqrt(count)) %>%
  distinct() %>%
  filter(type %in% c("p.inf", "p.cut", "p.par", "poten")) %>%
  distinct()
```

```{r, echo = F, eval = F}
stubble.brome %>%
  filter(location == "g",
         distance %in% c("20", "5"),
         year == "2023",
         collection == "fall")
```

@@

</body>
</html>
```
<!-- ![North Road, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/nnns-min.png?raw=true) -->

**Note:**\
- In 2023, the field south of North Road was fallow, so no stubble infestation data was collected from the field south of North Road.

@@

</body>
</html>
```
<!-- ![Gardiner Road, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/gardiner%20road-min.png?raw=true) -->

@@

</body>
</html>
```
<!-- ![Harvest & Sunset Road Instersection, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/harvest%20road-min.png?raw=true) -->

@@

</body>
</html>
```
<!-- ![Kolin Road, Moccasin, MT (2023)](https://github.com/jstrand894/Website/blob/main/kolin%20road-min.png?raw=true) -->
